The importance of transient resonances in extreme-mass-ratio inspirals

### 2016-08-27 res_char.tex
Adding self-force refs

\section{Introduction}
\pcm{The paper is very nice and the result is very important bcs it closes and open topic about the possible bias introduced by resonances in EMRI PE. General comments: (1)check acronyms along the text, in particular gravitational wave and GW, EMRI, etc....!!, (2) we don't mention anything about the astrophysical implications in the intro. It would be nice to include a couple of sentences. (3) I'll emphasise more the final result in the conclusions. }

@@

Geodesic motion in Kerr spacetime can be described by use of the action--angle formalism~\cite{Goldstein2002}. % Chapter 10
We consider a body of mass $\mu$ orbiting a BH of mass $M$, with $\eta = \mu/M \ll 1$,\footnote{To first order, the mass ratio $\eta$ is the same as the symmetric mass ratio $\mu M/(\mu+M)^2$.} and describe the motion in the directions of the standard Boyer--Lindquist coordinates $\{t,r,\theta,\phi\}$~\cite{Boyer1967} using generalised angle variables $q_\alpha = \{q_t,q_r,q_\theta,q_\phi\}$~\cite{Hinderer2008}. We denote the first integrals of the geodesic motion, the generalised action variables, by $J_\alpha$. These are some combination of the energy per unit mass $E$ and the axial angular momentum per unit mass $L_z$ of the orbit, which arise from isometries of the metric in $t$ and $\phi$, and the Carter constant per unit mass squared $Q$~\cite{Carter1968}, which is related to the separability of the equations of motion in $r$ and $\theta$. The system evolves following~\cite{Flanagan2012}
\begin{subequations}
\label{eq:Mino-E-o-M}
\begin{align}
\diff{q_\alpha}{\lambda} = {} & \omega_\alpha(\boldsymbol{J}) + \eta g_\alpha^{(1)}(q_r,q_\theta,\boldsymbol{J}) + \order{\eta^2}, \\
\diff{J_\alpha}{\lambda} = {} & \eta G_\alpha^{(1)}(q_r,q_\theta,\boldsymbol{J}) + \order{\eta^2},
\end{align}
\end{subequations}
where $\lambda$ is Mino time~\cite{Mino2003} \pcm{not everyone is familiar with this term. Besides, Mino does't like it. We could consider calling it "effective time" or similar} \cplb{with apologies to Mino, I think we're stuck with it}, and the forcing functions $g_\alpha^{(1)}$ and $G_A^{(1)}$ originate from the first-order self-force \pcm{this implies that there are  second, etc orders, we need to mention it and cite appropriately}\cplb{Suggestions for citations?}. By working with $\lambda$ instead of proper time $\tau$, the radial and polar motions decouple. At zeroth order in the mass ratio we recover the limit of purely geodesic motion: the integrals of the motion are actually constants and the angle variables evolve according to their associated frequencies $\omega_\alpha$.

@@

The jump in orbital parameters depends sensitively on the relative phase of radial and poloidal motions. This can be illustrated using an ensemble of orbits with different orbital phases $\psi_{\theta_-}$. According to \eqnref{delta-I-a}, the jumps should oscillate as a function of the phase $q$.\footnote{The overlaps for all of these different phases are similar, clustering around $0.7$, as expected from matching the post-resonance region of the waveform.} Therefore, assuming that the lowest harmonic dominates, plotting a jump in one parameter against another should trace out an ellipse. We find that this is the case; in \figref{resjump-vs-q} we plot resonant jumps as a function of the phase $q$ constructed from the $\Delta E\sub{jump}$--$\Delta Q{\mathrm{jump}}$ ellipse. The jumps in $E$ and $L_z$ are approximately in phase, but those in $Q$ are found to be offset~\cite{Flanagan2012a}; this means that for every value of $q$, there is always a resonance jump in at least one parameter.

>>>>

\section{Introduction}

@@

Geodesic motion in Kerr spacetime can be described by use of the action--angle formalism~\cite{Goldstein2002}. % Chapter 10
We consider a body of mass $\mu$ orbiting a BH of mass $M$, with $\eta = \mu/M \ll 1$,\footnote{To first order, the mass ratio $\eta$ is the same as the symmetric mass ratio $\mu M/(\mu+M)^2$.} and describe the motion in the directions of the standard Boyer--Lindquist coordinates $\{t,r,\theta,\phi\}$~\cite{Boyer1967} using generalised angle variables $q_\alpha = \{q_t,q_r,q_\theta,q_\phi\}$~\cite{Hinderer2008}. We denote the first integrals of the geodesic motion, the generalised action variables, by $J_\alpha$. These are some combination of the energy per unit mass $E$ and the axial angular momentum per unit mass $L_z$ of the orbit, which arise from isometries of the metric in $t$ and $\phi$, and the Carter constant per unit mass squared $Q$~\cite{Carter1968}, which is related to the separability of the equations of motion in $r$ and $\theta$. The system evolves following~\cite{Flanagan2012}
\begin{subequations}
\label{eq:Mino-E-o-M}
\begin{align}
\diff{q_\alpha}{\lambda} = {} & \omega_\alpha(\boldsymbol{J}) + \eta g_\alpha^{(1)}(q_r,q_\theta,\boldsymbol{J}) + \order{\eta^2}, \\
\diff{J_\alpha}{\lambda} = {} & \eta G_\alpha^{(1)}(q_r,q_\theta,\boldsymbol{J}) + \order{\eta^2},
\end{align}
\end{subequations}
where $\lambda$ is Mino time~\cite{Mino2003}, and the forcing functions $g_\alpha^{(1)}$ and $G_A^{(1)}$ originate from the first-order self-force.\footnote{For a discussion of the second-order self-force, see \cite{Rosenthal2006,Pound2012,Gralla2012}.} By working with $\lambda$ instead of proper time $\tau$, the radial and polar motions decouple. At zeroth order in the mass ratio we recover the limit of purely geodesic motion: the integrals of the motion are actually constants and the angle variables evolve according to their associated frequencies $\omega_\alpha$.

@@

The jump in orbital parameters depends sensitively on the relative phase of radial and poloidal motions. This can be illustrated using an ensemble of orbits with different orbital phases $\psi_{\theta_-}$. According to \eqnref{delta-I-a}, the jumps should oscillate as a function of the phase $q$.\footnote{The overlaps for all of these different phases are similar, clustering around $0.7$, as expected from matching the post-resonance region of the waveform.} Therefore, assuming that the lowest harmonic dominates, plotting a jump in one parameter against another should trace out an ellipse. We find that this is the case; in \figref{resjump-vs-q} we plot resonant jumps as a function of the phase $q$ constructed from the $\Delta E\sub{jump}$--$\Delta Q\sub{jump}$ ellipse. The jumps in $E$ and $L_z$ are approximately in phase, but those in $Q$ are found to be offset~\cite{Flanagan2012a}; this means that for every value of $q$, there is always a resonance jump in at least one parameter.
